The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-06-29 envolve.tex
add reinforcement learning
完成摘要初稿

Elo Rating System\cite{Elo1978} is a classic rating system for the ranking of chessplayer, most modern rating systems are derived from Elo's model:

@@

\subsection{Reinforcement Learning and Control} % (fold)
\label{sub:reinforcement_learning_and_control}
test figure

>>>>

Elo Rating System\cite{Elo1978} is a classic rating system for the ranking of chess-player, most modern rating systems are derived from Elo's model:

@@

### 2016-06-29 head.tex
完成摘要初稿

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In Cloud Manufacturing, provider publish manufacturing resource as service on the platform for demander to search and purchase it as product. This shopping model makes it possible to centralised manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
Thus the servitization and optimization of manufacturing resource constitutes a central issue to  in such manufacturing ecosystem.

% 提出了 Cloud Manufacturing Ecosystem 概念，建立相应的生态系统模型，从系统中的各个角色，（需要一个指标）建立系统动力学方程。通过仿真手段验证模型，结合已有的云平台原型系统，给出相关应用。
% 云制造的实施和应用提供了一种全新的制造业生态系统，该生态系统由成员（企业用户、管理员）及环境（）组成。为了探究生态系统中，制造业的运作模式（相关决策），优化产业链，形成良性发展的制造生态，通过基于Agent 的建模，来刻画该系统中的个体行为，并通过仿真技术，模拟演化规律。

% 云制造生态系统中，不同的企业具有不同的生态位
% 该系统的输入
% 输出
% 调控方式

% 通过仿真，我们发现。。。

@@

 % Supplier evaluation and selection constitutes a central issue in supply chain management (SCM). How- ever, the data on which to base the corresponding choices in real life problems are often imprecise or vague, which has led to the introduction of fuzzy approaches. Predictive intelligent-based techniques, such as Artificial Neural Network (ANN) and Adaptive Neuro Fuzzy Inference System (ANFIS), have been recently applied in different research fields to model fuzzy multi-criteria decision processes where the understanding and learning of the relationships between the input and output data are the key to select suitable solutions. In this paper, a hybrid ANFIS-ANN model is proposed to assist managers in their sup- plier evaluation process. After aggregating the data set through the Analytical Hierarchy Process (AHP), the most influential criteria on the suppliers’ performance are determined by ANFIS. Then, Multi-Layer Perceptron (MLP) is used to predict and rank the suppliers’ performance based on the most effective criteria. A case study is presented to illustrate the main steps of the model and show its accuracy in prediction. A battery of parametric tests and sensitivity analyses has been implemented to evaluate the overall performance of several models based on different effective criteria combinations.

In this paper, ....

@@

% The research was conducted in three steps: (1) existing concepts and models for industrial sustainability were reviewed and environmental practices in manufacturing were collected and analysed; (2) gaps in knowledge and practice were identified; (3) the outcome is a manufacturing ecosystem model based on industrial ecology (IE)
% 关键是系统动力学模型的建立。

>>>>

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In Cloud Manufacturing, user do manufacturing business with well-designed platform framework, where provider publish manufacturing resource as service for demander to search and purchase it as product. This shopping model makes it possible to centralized manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.

However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
Thus the way that each provider transforms his/her resource into product with servitization and optimization, constitutes a central issue in such manufacturing ecosystem, all these servitization and optimization activities brings the transition to the individual in the ecosystem, then the manufacturing service pattern will appear with these transitions.

In this paper, we proposed an operation model for users to support their transitions by means of expanding or shrinking their scope of manufacturing service in the manufacturing ecosystem, and we also proposed an adjustment approach, which depends on the ranking value of user, for the system to restrict the expanding or shrinking procedure and to control the number of users. Gradually this adjustment will guide evolution of the ecosystem, meanwhile, good service pattern will be discovered for the user to survival.

With the help of Repast Simphony, we designed an agent-based model to simulate the evolution process of the ecosystem.
As the simulation output, manufacturing resource's quality is improving and its diversity is increasing with the evolution process goes by, the emergence pattern of service and resource optimization implies the effectiveness and validity of the proposed operation model and adjustment approach, user's rank-based transitions does improve the utilization of manufacturing resource.

@@

% Supplier evaluation and selection constitutes a central issue in supply chain management (SCM). How- ever, the data on which to base the corresponding choices in real life problems are often imprecise or vague, which has led to the introduction of fuzzy approaches. Predictive intelligent-based techniques, such as Artificial Neural Network (ANN) and Adaptive Neuro Fuzzy Inference System (ANFIS), have been recently applied in different research fields to model fuzzy multi-criteria decision processes where the understanding and learning of the relationships between the input and output data are the key to select suitable solutions. In this paper, a hybrid ANFIS-ANN model is proposed to assist managers in their sup- plier evaluation process. After aggregating the data set through the Analytical Hierarchy Process (AHP), the most influential criteria on the suppliers¡¯ performance are determined by ANFIS. Then, Multi-Layer Perceptron (MLP) is used to predict and rank the suppliers¡¯ performance based on the most effective criteria. A case study is presented to illustrate the main steps of the model and show its accuracy in prediction. A battery of parametric tests and sensitivity analyses has been implemented to evaluate the overall performance of several models based on different effective criteria combinations.

@@

% The research was conducted in three steps: (1) existing concepts and models for industrial sustainability were reviewed and environmental practices in manufacturing were collected and analysed; (2) gaps in knowledge and practice were identified; (3) the outcome is a manufacturing ecosystem model based on industrial ecology (IE)
